---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/UBESP-DCTV/imthcm.svg?branch=master)](https://travis-ci.org/UBESP-DCTV/imthcm.svg?branch=master)
[![Coverage status](https://codecov.io/gh/UBESP-DCTV/imthcm/branch/master/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/imthcm?branch=master)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/oalfbbranadcxwp6?svg=true)](https://ci.appveyor.com/project/CorradoLanera/imthcm)


# imthcm

## Introduction

**REMEDIO** stands for “**RE**generating mixed-use **MED** urban communities
congested by traffic through **I**nnovative low carbon mobility s**O**lutions”.

**REMEDIO** is funded by Interreg MED Program 2014-2020 through the European
Regional Developed Fund (ERDF) (<https://remedio.interreg-med.eu/>)

**REMEDIO** implements concrete actions to relieve traffic congestion in
middle-size Mediterranean cities where territorial institutions, supported by
research/technical partners, are involved as beneficiary partners.

**REMEDIO** is a testing project and is developed in 3 steps.

- First Territorial partners implement soft actions on low carbon mobility
  solutions (Sustanaible Urban Mobility Plans  in Treviso, Split and Loures,
  Bike sharing Network in Spit and Treviso; bicycle parking areas in Loures,
  bus rapid transit, multi modal public transport optimizations, green-taxiway,
  safety road infrastructure for bus stops in Thessaloniki).
  
- Second Scientific partners jointly implement an Integrated Modelling Tool to
  assess the present and future scenarios road performance in terms of energy
  and freight transport efficiency, noise impact, air pollution, **cost** &
  **health** effects.
  
- In the meanwhile, as third step, the city communities are engaged in testing
  an operational path towards a participatory governance such as “horizontal
  condominiums” or “road contracts” that should lead to higher environmental
  and mobility performances.

The goal of imthcm is to provide the **health** and **cost** modules for the
Integrated Modelling Tool of REMEDIO project.

## Installation

<!-- You can install the released version of imthmcm from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("imthmcm") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/)
with the following procedure:

- If you do not have the `devtools` package installed, please install it by
```{r, eval = FALSE}
install.packages("devtools", dependencies = TRUE)
```

- Now you can install the package from github 
```{r, eval = FALSE}
devtools::install_github("UBESP-DCTV/imthcm")
```

- and load it
```{r}
library(imthcm)
```

- Once installed and loaded you can use the `check_package()` and
  `please_install()` functions (which work only in interactive mode) to
  check if you have all the needed package installed and updated:
```{r, eval = FALSE}
check_pkg()

## Furter check for a particouar version of mgcv
if (packageVersion('mgcv') < 1.8.23) {
  please_install('mgcv', dependencies = TRUE)
}
```

Now you have installed and loaded all the necessary package for the modules.
The modules and the example files are in the package folder `inst/modules/`
and `inst/test_xml/` respectively. Once installed, those folder where 
put one level up, i.e. out of the `inst/` folder. You can have a direct
access to those going into the corresponding system folder:

```{r}
system.file('modules', 'hm.R', package = 'imthcm')
system.file('modules', 'cm.R', package = 'imthcm')

system.file('test_xml', 'test_event_history.xml',   package = 'imthcm')
system.file('test_xml', 'test_weather_history.xml', package = 'imthcm')
system.file('test_xml', 'test_weather_new.xml',     package = 'imthcm')
system.file('test_xml', 'test_cost_data.xml',       package = 'imthcm')
```

To run the modules on a linux machine, you have to let the system know that
they are "executable" by
```
chmod +x path/to/modules/folder/hm.R
chmod +x path/to/modules/folder/cm.R
```
Note, you can copy those files and run them everywhere you prefer: the
modules automatically load the package and find inside every function they
need. So suppose you have the Health Module in `./` and the examples XML
files in `./test_xml/` folder respectively. So, e.g., you can run the module
with italian defaults training data and models by the following command

```
./hm.R -d -n ./test_xml/test_weather_new.xml -o my_hm_output.xml -f my_hm_figure.png
```

Or using the test XML history files (and also changing the figure device) by

```
./hm.R -w ./test_xml/test_weather_history.xml -e ./test_xml/test_event_history.xml -n ./test_xml/test_weather_new.xml -o my_hm_output.xml -f my_hm_figure.pdf
```

The same for the cost module, which should recieve in imput the output of 
the health modules. Hence, continuing our examples, cm can be run using
default cost data by

```
./cm.R -e my_hm_output.xml -d -o my_cm_output.xml -f my_cm_figure.png
```

or providing custom cost data by

```
./cm.R -e my_hm_output.xml -c ./test_xml/test_cost_data.xml -o my_cm_output.xml -f my_cm_figure.png
```

(Please note that the last to command line will provide exactly the same
output because the default cost data are the ones stored in
`./test_xml/test_cost_data.xml`)


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
to <https//github.com/UBESP-DCTV-imthcm/issues>
